\ttitle

### 2013-02-01 Chapters/Chapter2.tex
Finished text on PCA. Figures still needed

This section will give an introduction and in-depth analysis of temporal 
segmentation. test. nog een test. test

@@

The workings of the PCA \cite{smith2002tutorial} relies on the concepts of 
standard deviation, 
covariance, eigenvectors and eigenvalues of matrices. These concepts will be 
discussed very briefly \footnote{For a more in-depth discussion we would like 
to refer the reader to \cite{jolliffe2005principal}}. The standard deviation 
of a set is an measure for the 
spread around the mean for a single dimension, or feature. The covariance 
between two features (dimensions of the data points) indicates how they are 
related; when positive the two 
features will increase together; when negative one will decrease when the 
other increases and when zero they are unrelated. The covariance matrix gives 
all the covariances for all pairs of features. This matrix is symmetrical 
about the diagonal and the values on the diagonal are the variances for each 
feature. For this matrix the eigenvectors can be computed. Eigenvectors have 
the characteristic that when they multiply a matrix, the resulting vector is a 
multiple of the eigenvector. The amount by which it is the multiple is the 
Eigenvalue. This is illustrated in formulae \ref{eq:no-eigenvector} and 
\ref{eq:eigenvector}. The second formula shows an Eigenvector and its 
associated Eigenvalue, 4. The vector in the first formula is not an 
Eigenvector.

@@

It are these Eigenvectors and Eigenvalues that makes PCA possible. Given a 
matrix of $n \times n$ (only square matrices have Eigenvectors), $n$ 
Eigenvectors can be found. Each Eigenvector is perpendicular, or orthogonal, 
to the others. The Eigenvectors combined describes the lines over which the 
data is plotted. The Eigenvector with the largest Eigenvalue is the 
\emph{principal} component of the data set. It is said that it is the most 
significant dimension. Thus the Eigenvectors, and thereby the features or 
dimensions of the data set, can be sorted on significance by the Eigenvalues.

With this ordering there are a few applications possible. The first is to just 
make a (comprehensible) representation of the data. The Eigenvectors describe 
the cloud of data points and thus a

@@

***
[purpose: dimensionality reduction, most discriminative dimensions. Difference 
in dimensionality.]

>>>>

This section will give an introduction and in-depth analysis of temporal 
segmentation.

@@

The following steps are performed, which are explained below and illustrated 
in figure *** [add figure with plot of sets] \ref{}:
\begin{enumerate}
	\item \textbf{Gather data} and represent them in a chosen number of 
	features,
	\item \textbf{Subtract mean} to center the data around the axis. The new 
	data set will have mean zero,
	\item \textbf{Generate covariance matrix} by calculating all pairwise 
	feature variances,
	\item \textbf{Calculate Eigenvectors and Eigenvalues} of the covariance 
	matrix. The Eigenvectors are then normalized to make further calculations 
	easier,
	\item \textbf{Generate feature vector} which indicated which features are 
	characteristic or meant to keep in de data set, by comparing the 
	Eigenvalues. 
\end{enumerate}

The workings of the PCA \cite{smith2002tutorial} relies on the concepts of 
standard deviation, variance,
covariance, eigenvectors and eigenvalues of matrices. These concepts will be 
discussed very briefly \footnote{For a more in-depth discussion we would like 
to refer the reader to \cite{jolliffe2005principal}}. The standard deviation 
and variance
of a set are measures for the 
spread around the mean for a single dimension, or feature. The covariance 
between two features (dimensions of the data points) indicates how they are 
related; when positive the two 
features will increase together; when negative one will decrease when the 
other increases and when zero they are unrelated. The covariance matrix gives 
all the covariances for all pairs of features. This matrix is symmetrical 
about the diagonal and the values on the diagonal are the variances for each 
feature. For this matrix the eigenvectors can be computed. Eigenvectors have 
the characteristic that when they multiply a matrix, the resulting vector is a 
multiple of the Eigenvector. The amount by which it is the multiple is the 
Eigenvalue. This is illustrated in formulae \ref{eq:no-eigenvector} and 
\ref{eq:eigenvector}. The second formula shows an Eigenvector 
$ \left( \begin{smallmatrix} 
3 \\ 2 \end{smallmatrix} \right)$ and its 
associated Eigenvalue, 4. The vector in the first formula is not an 
Eigenvector.

@@

It are these Eigenvectors and Eigenvalues that makes PCA possible. Given a 
matrix of size $n \times n$ (only square matrices have Eigenvectors), $n$ 
Eigenvectors can be found. Each Eigenvector is perpendicular, or orthogonal, 
to the others. The Eigenvectors combined describes the lines over which the 
data is plotted. The Eigenvector with the largest Eigenvalue is the 
\emph{principal} component of the data set. It is said that it is the most 
significant feature. Thus the Eigenvectors, and thereby the features or 
dimensions of the data set, can be sorted on significance by the Eigenvalues.

With this ordering there are a few applications possible. The first is to just 
make a (comprehensible) representation of the data. The Eigenvectors describe 
the cloud of data points and thus are a compressed representation of the data. 
When the original data points are to be compressed, it is possible to remove 
the least significant features and reconstruct the data points from the 
resulting Eigenvectors. This will yield in a lossy compression. *** [figure to 
illustrate]. An extension of this application is to determine the number of 
features needed to keep the compression within a certain error criterion, as 
used in \cite{barbivc2004segmenting}. Sets of data can then be distinguished 
by the number of features needed to describe the points.

@@

### 2013-02-01 main.tex
Finished text on PCA. Figures still needed

\usepackage[square, numbers, comma, sort&compress]{natbib} % Use the natbib reference package - read up on this to edit the reference style; if you want text (e.g. Smith et al., 2012) for the in-text references (instead of numbers), remove 'numbers' 
\hypersetup{urlcolor=blue, colorlinks=true} % Colors hyperlinks in blue - change to black if annoying
\title{\ttitle} % Defines the thesis title - don't touch this

>>>>

\usepackage[square, numbers, comma, sort&compress]{natbib} % Use the natbib 
%reference package - read up on this to edit the reference style; if you want 
%text (e.g. Smith et al., 2012) for the in-text references (instead of 
%numbers), remove 'numbers' 
\hypersetup{urlcolor=blue, colorlinks=true} % Colors hyperlinks in blue - 
%change to black if annoying
\title{\ttitle} % Defines the thesis title - don't touch this
